### 2020-10-14 priority-gv.tex
Draft version! :D

@@

Terms are typed by a judgement $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$. Typing is standard for the linear $\lambda$-calculus. Linearity is ensured by splitting environments on branching rules, requiring that the environment in the variable rule consists of just the variable, and the environment in the constant and unit rules are empty. The constants $\tm{K}$ are typed using type schemas, and embedded using \LabTirName{T-Const}.

@@

Configurations are typed by a judgement $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$. Configuration typing is based on the standard typing for GV. Terms are embedded either as main or as child threads. The priority bound from the term typing is discarded, as configurations contain no further sequential actions. Main threads are allowed to return a value, whereas child threads are required to return the unit value. Sequents are annotated with a flag $\phi$, which ensure that there is at most one main thread.

>>>>

Structural congruence satisfies the following axioms: $\LabTirName{SC-LinkSwap}$ allows swapping channels in the link process. $\LabTirName{SC-ResLink}$ allows restriction to applied to link which is structurally equivalent to the terminated process, thus allowing elimination of unnecessary restrictions. $\LabTirName{SC-ResSwap}$ allows swapping channels and $\LabTirName{SC-ResComm}$ states that restriction is commutative. $\LabTirName{SC-ResExt}$ is the standard scope extrusion rule. Rules $\LabTirName{SC-ParNil}$, $\LabTirName{SC-ParComm}$ and $\LabTirName{SC-ParAssoc}$ state that parallel composition uses the terminated proceess as the neutral element; it is commutative and associative.

@@

Terms are typed by a judgement $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$, which states that ``a term $\tm{M}$ has type $\ty{T}$ and an upper bound on its priority $\cs{p}$ under the typing environment $\ty{\Gamma}$''. Typing is standard for the linear $\lambda$-calculus. Linearity is ensured by splitting environments on branching rules, requiring that the environment in the variable rule consists of just the variable, and the environment in the constant and unit rules are empty. The constants $\tm{K}$ are typed using type schemas, and embedded using \LabTirName{T-Const}.

@@

Configurations are typed by a judgement $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, which states that ``a configuration $\tm{\conf{C}}$ with flag $\phi$ is well-typed under typing environment $\ty{\Gamma}$''. Configuration typing is based on the standard typing for GV. Terms are embedded either as main or as child threads. The priority bound from the term typing is discarded, as configurations contain no further sequential actions. Main threads are allowed to return a value, whereas child threads are required to return the unit value. Sequents are annotated with a flag $\phi$, which ensure that there is at most one main thread.
